Replication and Extension of Analyses Regarding Effects of Highly Restrictive Abortion Policies

### 2021-12-16 paper_replication.Rmd
Update paper_replication.Rmd

---
title: "paper_replication"
output: pdf_document
---
## Abstract
### Importance
In the United States, many state legislatures have enacted a range of laws limiting access to abortions.  These laws limit access to crucial healthcare and have impacts on mortality, fertility, and birth rates across the country.

@@

### Exposures
In the replication, the exposures are a state-level highly restrictive abortion legislation as defined by 3 or more out of 4 common types of abortion restrictions and county-level distance to facilities performing abortions (in miles).  For the extension, the exposures are the number of types of abortion legislation and the distance to facilities performing abortion (in miles).

@@

### Results
Our replication confirms the primary result of Brown et al. (2020). We found that highly restrictive legislation is associated with 0.814 fewer abortions per 1,000 women without adjusting for distance to providers, and 0.649 fewer abortions per 1,000 women when adjusting for distances to providers.  These effects are somewhat larger in magnitude than the effects calculated by Brown et al., which were -0.48 (95% CI, -0.92 to -0.04) and -0.44 (95% CI, -0.85 to -0.03), but our estimates were well within their reported 95% confidence intervals. Infant mortality rates were positively associated with abortion restrictions, and these associations were statistically significant even after adjusting for distance from providers.  The maternal and fetal mortality rates were not statistically significant.

### Conclusions and Relevance
Our analysis confirms the results of Brown et al. showing a negative association between restrictive abortion legislation and abortion rates based on both the 18 states they analyized and based on data from all 50 states.  We furthered the analysis to additional outcomes and found positive associations between restrictions and infant death rates.

@@

>>>>

---
title: "Replication and Extension of Analyses Regarding Effects of Highly Restrictive Abortion Policies"
output: pdf_document
---
## Abstract
### Importance
In the United States, many state legislatures have enacted a range of laws limiting access to abortions.  These laws limit access to crucial healthcare and have impacts on mortality, fertility, and birth rates across the country.

@@

### Exposures
In the replication, the exposures are state-level highly restrictive abortion legislation as defined by 3 or more out of 4 common types of abortion restrictions and county-level distance to facilities performing abortions (in miles).  For the extension, the exposures are the number of types of abortion legislation and the state-level average distance to facilities performing abortion (in miles).

@@

### Results
Our replication confirms the primary result of Brown et al. (2020). We found that highly restrictive legislation is associated with 0.814 fewer abortions per 1,000 women without adjusting for distance to providers, and 0.649 fewer abortions per 1,000 women when adjusting for distances to providers.  These effects are somewhat larger in magnitude than the effects calculated by Brown et al., which were -0.48 (95% CI, -0.92 to -0.04) and -0.44 (95% CI, -0.85 to -0.03), but our estimates were well within their reported 95% confidence intervals. Infant mortality rates were positively associated with abortion restrictions, and these associations were statistically significant even after adjusting for distance from providers. The maternal and fetal mortality rates as well as the birth rates were not statistically significant after adjusting for distance from providers.

### Conclusions and Relevance
Our analysis confirms the results of Brown et al. showing a negative association between restrictive abortion legislation and abortion rates based on both the 18 states they analyized and based on data from all 50 states.  We furthered the analysis to additional outcomes and found positive associations between restrictions and infant death rates, while restrictions do not have a significant association with birth rates or maternal or fetal mortality rates after adjusting for distance to providers.

@@

Data on the percentage of democratic votes by county in the most recent (2008) presidential election was retrieved from the Harvard Dataverse.
